---
title: "Homework-1-Group-19"
author: "Abhinav, Mukul, Vijay"
date: "17/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Homework group - 19 (Abhinav, Mukul, Vijay)


## Data and project setup

* Installing styler to maintain code consistency

```{R}
# install.packages("styler")
```

* Loading libraries

```{R}
# Loading the required libraries

library(dplyr)
library(stringr)
library(readr)

```

* Reading all datasets, and storing them into data frames

```{R}
# Dataframe variables
df_fm <- read.csv("fm.csv")
df_wine <- read.csv("wine_data.csv")
df_keywords <- read_csv("keyword_data.csv")

# Dimension variables
dim_farmers_market <- dim(df_fm)
dim_wine <- dim(df_wine)
dim_keywords <- dim(df_keywords)

# Number of records / dimensions for observations
print(paste("The dimensions for the farmers market dataset are:",dim_farmers_market[1],dim_farmers_market[2]))

print(paste("The dimensions for the wines dataset are:",dim_wine[1],dim_wine[2]))

print(paste("The dimensions for the key dataset are:",dim_keywords[1],dim_keywords[2]))

```

## 1. Questions on farmers market dataset


1.1  Compute the number of farmers market in the United States

```{R}
# Naively, Taking number of unique market names can be taken as an assumption, and taken of as the answer
unq_markets <- unique(df_fm$MarketName)

# However this gives the answer as [1] 8243 and the observations are 8801
incorrect_ans <- length(unq_markets)

# On further inspection of the data, some of the different states have the same name of markets.

# Method 1 -> Using FMID as primary key

# Since Farmers market names are not unique, we can calculate number of unique FMID.
num_unq_markets <- length(unique(df_fm$FMID))

print(paste("The number of unique farmer markets based on FMID:",num_unq_markets))

# Method 2 -> Generating our own primary key
# In case we didn't have a primary key in the dataset, we can generate our own.

# To do the same, we add a new identifier UNQ_ID, which is the combination of the Market Name, City , County and State and use this as our primary identifier
df_fm$UNQ_ID <- paste(trimws(df_fm$MarketName) , trimws(df_fm$city), trimws(df_fm$County) , trimws(df_fm$State))

num_unq_markets_2 <- length(df_fm$UNQ_ID)

print(paste("The number of unique farmer markets based on combination of Name, City, County and State are: ",num_unq_markets_2))



```

1.2 Write a code to compute the number of farmers markets by state and arrange
them in descending order of number of farmers market.

* Method 1 <- Subsetting all states within fm dataset by using list of unique state

```{R}

## Create a vector containing state names
list_of_states <- unique(df_fm$State)

## Initialize a vector having length equal to number of state
count_of_markets <- 1:length(list_of_states)

## Apply a for loop to iterate over every state name 
for (i in 1:length(list_of_states)){
   ## Find the number of markets in a state and store in a variable
  count_of_markets_in_state <- dim(subset(df_fm, df_fm$State==list_of_states[i]))[1]
   ## Store the value of variable at the same index as of state  
  count_of_markets[i] <- count_of_markets_in_state
}

## Create a new data frame where the column values would be 2 vectors created above
temp_df <- data.frame("State"=list_of_states, "Count_Of_Market"=count_of_markets)

## sort the dataframe on number of markets
fm_by_states_one <- temp_df[order(temp_df$Count_Of_Market, decreasing = TRUE),]

fm_by_states_one

```

* Method 2 <- Iterating over every unique state and farmers market data

```{R}

# Make a blank dataframe with unique states and count initialized as 0
fm_by_states_two <- data.frame(State=unique(df_fm$State),cnt = c(0))


# Looping over unique states
for (i in 1:dim(fm_by_states_two)[1]){
   # Looping over all farmer markets data
  for (j in 1:dim(df_fm)[1]) {
     # If a match is encountered with current state, increase count by 1
   if (fm_by_states_two[i,'State'] == df_fm[j,'State']) {
     fm_by_states_two[i,'cnt'] <- fm_by_states_two[i,'cnt'] + 1
   }
}
}

# Sort the dataframe
fm_by_states_two <- fm_by_states_two[order(fm_by_states_two$cnt,decreasing =  T),]

fm_by_states_two

```

* Method 3 -> Using DPLYR

```{R}
# Dplyr has in built functions which can help do the same with a few lines of code

fm_by_states_three <- group_by(df_fm, State ) %>% summarize(cnt = n()) %>% arrange(desc(cnt), .by_group = T)

fm_by_states_three

```

1.3 Write a code to compute the number of farmers market by cities in
Massachusetts and display the top five cities

* Method 1 <- Iterating over all farmer markets data and adding data where city matches

```{R}

# Making a copy of the dataframe, to avoid data iconsistency issues
df_fm_ma <- df_fm

# Creating an empty data frame with City and count as columns
df_fm_MA_City <- data.frame(City=character(),count=as.numeric())

# Removing empty values from the dataframe
df_fm_ma <- subset(df_fm_ma ,df_fm_ma$city != "")

# String manipulation to ensure consistent name of cities
# Removing trailing / leading whitespace
df_fm_ma$city <- trimws(df_fm_ma$city)

# Converting city to lower case
df_fm_ma$city <- tolower(df_fm_ma$city)

# Iterating over farmers market dataset
for (i in 1:dim(df_fm_ma)[1]) {
   # If state matches Massachusetts
   if (df_fm_ma[i,"State"] == "Massachusetts") {
      # Current city
      current_city <- df_fm_ma[i,"city"]
      # Check if any city matches current city
      if (any(df_fm_MA_City$City == current_city )  ) {
         # Index where the city matches
         city_index = which(df_fm_MA_City$City == current_city)
   # Increment count of city by 1
   df_fm_MA_City[city_index,'count']  <-  as.numeric(df_fm_MA_City[city_index,'count'])  + as.numeric(1)
      } else {
         # If city doesn't exist initialize it by 1
         df_fm_MA_City[nrow(df_fm_MA_City) + 1,] = c(current_city , as.numeric(1))
      }
   }
   
}

# Convert count to numeric
df_fm_MA_City$count <- as.numeric(df_fm_MA_City$count)

# Sort the values
answer_one <- df_fm_MA_City[order(df_fm_MA_City$count,decreasing=T),]

# Answer is the top 5 values
answer_one <- head(answer,5)

answer_one
```

* Method 2 <- Using subset to match cities while iterating

```{r}
## Filter data on MA state
ma_state = subset(df_fm, df_fm$State=="Massachusetts")

## Trimming the extra spaces and lowercase the column 'city'
ma_state$city <- trimws(ma_state$city)
ma_state$city <- str_to_lower(ma_state$city)

## Drop rows where city is null
ma_state <- ma_state[!is.na(ma_state$city),]

## Create a vector containing the name of cities
list_of_cities <- unique(ma_state$city)
## Create a vector having length equal to the number of cities
count_of_markets <- 1:length(list_of_cities)

## Iterate over name of cities
for (i in 1:length(list_of_cities)){
  ## Find the number of markets in a city and store in a variable
  count_of_markets_in_city <- dim(subset(ma_state, ma_state$city==list_of_cities[i]))[1]
  ## Store the value of variable at the same index as of city  
  count_of_markets[i] <- count_of_markets_in_city
}

## Create a new data frame where the column values would be 2 vectors created above
df <- data.frame("City"=list_of_cities, "Count_Of_Market"=count_of_markets)

df <- df[order(df$Count_Of_Market, decreasing = TRUE),]

# Showing the answer
head(df, 5)
```



1.4 - Write a code to show the top 5 states by number of farmers market that offers coffee

```{r}

## Filter out farmers who offer coffee
coffee_df <- df_fm %>%
  filter(Coffee=="Y")

## String manipulations to ensure consistency
coffee_df$city <- trimws(coffee_df$city)
coffee_df$city <- str_to_lower(coffee_df$city)

## Group on State name and take the count of number of farmers market to get the result
answer <- coffee_df %>%
  group_by(State) %>%
  summarise(Number_of_Markets = n())

## Sort the results on number of farmers market
answer <- answer[order(answer$Number_of_Markets, decreasing = TRUE),]
head(answer, 5)
```




2.1  Use the “designation” variable and calculate the number of 20 year old wine in
the dataset

* Method 1 -> Using regex with grep / str_which
```{R}


# There is some confusion whether "anniversary" keyword should be considered in the dataset as wine age

# Answer WITHOUT considering anniversary (using grep)
wine_twenty_without_anniversary <- df_wine[grep("(20 |20-|20th|20- )( )?(Y+|y+|Anos|anos|anni )",df_wine$designation,ignore.case = T),]

# Answer WITH anniversary (using str_which)
wine_twenty_with_anniversary <- df_wine[str_which(df_wine$designation,"(20 |20-|20th)( )?(Y+|y+|Anniver+|anniver+|Anos|anos|anni)"),]

# According to our observation of data, 20th Anniversary wine does NOT necessarily mean a 20 year old wine

print(paste("There are ", dim(wine_twenty_with_anniversary)[1],"wines if we consider 'anniversary' keyword as wine age."))

print(paste("There are ", dim(wine_twenty_without_anniversary)[1],"wines without considering 'anniversary' keyword as wine age."))

```

* Method 2 <- Using list of possible 20 year old wines to filter data

```{r}

## This result is producing 85 results which includes 'Anniversary' keyword as well

## Lowercase all the designation for uniformity and reduce redundancy 
df_wine$designation <- str_to_lower(df_wine$designation)

## Create a vector of possible strings
string_list <- c("20 years","20 year","20 yrs","20 yr","20 anos","20_years","20_year","20_yrs","20_yr","20_anos","20-years","20-year","20-yrs","20-yr","20-anos","20years","20year","20yr","20yrs","20anos","20 th anni","20th anni","20 anni")
temp_df <- data.frame()

## Iterate over all the possible strings and get rows after partial match
for (i in string_list){
  index <- str_which(df_wine$designation, i)
  answer <- df_wine[index,]
  temp_df <- rbind(temp_df,answer) 
}
## Drop duplicate rows (if any) 
final_df <- temp_df[!duplicated(temp_df),]

print(paste("There are ", dim(final_df)[1],"wines if we consider 'anniversary' keyword as wine age."))
```

3.1 Write an R code to extract keyword data from the above file and convert it to a weighted adjacency matrix. See the figure below to understand the process

* Method 1 
```{r}

## drop rows with null keywords
df_keywords1 = df_keywords[!is.na(df_keywords$`Keyword 1`),]
temp <- c()

## iterate over the keyword dataframe, pick each keyword and append it into the vector 
for (i in 1:dim(df_keywords1)[1] ){
  for ( j in 2:dim(df_keywords1)[2]){
    if (!is.na(df_keywords1[[i,j]])){
      temp <- c(temp,tolower( df_keywords1[[i,j]]))
    }
  }
}
## Drop duplicates from vector
temp<-unique(temp)

## Create a matrix with dimension equal to length of number of unique keywords
adjacency_matrix <- matrix(0, nrow = length(temp), ncol =length(temp) )

## Rename column and row names as the keywords
rownames(adjacency_matrix) <- c(temp)
colnames(adjacency_matrix) <- c(temp)

## Iterate over keyword dataframe and increment values in the empty matrix
n_rows = dim(df_keywords1)[1]
for (x in 1:n_rows){
  for (i in 2:length(df_keywords1)){
    for (j in 2:length(df_keywords1)){
      
      ## Find keyword 1 and keyword 2
      key1 <- tolower(df_keywords1[[x,i]])
      key2 <- tolower(df_keywords1[[x,j]])
      
      ## Key1 should not be equal to Key2 and either of them should not be null
      if ((!is.na(key1))&&(!is.na(key2))&&(key1!=key2)){
        adjacency_matrix[key1, key2] = adjacency_matrix[key1, key2]+1 
      }
    }
  }
}

print("The dataframe is below:")
sum(adjacency_matrix)
adjacency_df <- data.frame(adjacency_matrix)

adjacency_df
```


```{R}

library(tidyr)

df_keywords <- read.csv("keyword_data.csv")



# Pivot the table to longer form
longer_keywords <- df_keywords %>% pivot_longer(cols= starts_with("Keyword"), values_to="Keyword")

# Get all distinct keywords
unique_keywords <- distinct(longer_keywords,Keyword) 

# Remove the "" empty keyword
unique_keywords <- unique_keywords[!(unique_keywords$Keyword == ""),]

# Introduce a new CO_OCCURENCE variable to get the same data in wider form
unique_keywords$CO_OCCURRENCE <- 0

# Make the data available in wider form
wide_unique_keywords <- unique_keywords %>% pivot_wider(names_from  =Keyword,values_from=CO_OCCURRENCE,values_fill=0)


# Bind both wider and longer table together to get adjacency matrix
keyword_matrix <- bind_rows(unique_keywords,wide_unique_keywords)

# Dropping dummy column of co occurrence
keyword_matrix <- keyword_matrix[,!(names(keyword_matrix) %in% c("CO_OCCURRENCE"))]

# Assigning all values to 0
keyword_matrix[,c(2:249)] <- 0


## Solution 1

# Removing all blank observations
df_keywords <- df_keywords[!(df_keywords$Title == ""),]

# Combining all keywords for an article for easier analysis
df_keywords$COMBINED_KEYWORDS <-paste(trimws(df_keywords$Keyword.1) , trimws(df_keywords$Keyword.2) , trimws(df_keywords$Keyword.3) , trimws(df_keywords$Keyword.4)  , trimws(df_keywords$Keyword.5) , trimws(df_keywords$Keyword.6),                               trimws(df_keywords$Keyword.7)  , trimws(df_keywords$Keyword.8) , trimws(df_keywords$Keyword.9),
trimws(df_keywords$Keyword.10) , trimws(df_keywords$Keyword.11) , trimws(df_keywords$Keyword.2),sep="-"  )

df_keywords$COMBINED_KEYWORDS <- paste("-",df_keywords$COMBINED_KEYWORDS,"-",sep="")


# 
# Combining all keywords for an article for easier analysis
# df_keywords$COMBINED_KEYWORDS <-paste(trimws(df_keywords$`Keyword 1`) , trimws(df_keywords$`Keyword 2`) , trimws(df_keywords$`Keyword 3`) , trimws(df_keywords$`Keyword 4`)  , trimws(df_keywords$`Keyword 5`) , trimws(df_keywords$`Keyword 6`),                               trimws(df_keywords$`Keyword 7`)  , trimws(df_keywords$`Keyword 8`) , trimws(df_keywords$`Keyword 9`),
# trimws(df_keywords$`Keyword 10`) , trimws(df_keywords$`Keyword 11`) , trimws(df_keywords$`Keyword 12`),sep="-"  )

num_articles <- dim(df_keywords)[1]

unq_keywords = names(keyword_matrix)

# 1 Extra entry in matrix
num_keywords <- dim(keyword_matrix)[1] - 1





## To correct -> Loop over articles first, then matrix
# Loop over all articles
for (i in 1:num_articles) {
   current_article_keywords <- df_keywords[i,'COMBINED_KEYWORDS']
   # Loop over rows in adjacency matrix
   for( j in 1:num_keywords){
      
      current_row_keyword <- paste("-",keyword_matrix[j,1],"-",sep="")
      # Loop over columns in adjacency matrix
      for (k in 2:num_keywords) {
         # 
         current_col_keyword <- paste("-",unq_keywords[k],"-",sep="")
         
 if (current_article_keywords != "-------------" && current_col_keyword != current_row_keyword && (grepl(current_row_keyword,current_article_keywords,fixed = TRUE) && grepl(current_col_keyword,current_article_keywords,fixed = TRUE)) ) {
            keyword_matrix[j,k] <- keyword_matrix[j,k] + 1
         }
      }
   }
}

sum(keyword_matrix[,2:249])


```
